Bird beak's elaboration and exploration

### 2022-06-23 Analysis/02-mcmcmcglmmm_analysis.Rmd
Up todo

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
# for(i in 1:3) {
    load(paste0("../Data/Cluster/shapespace_passeriformes/param_chains/param_chain_passeriformes_50levels_chain", 1, ".rda"))
    param_chains[[1]] <- param_chain_passeriformes_50levels_chain1[[1]]
    load(paste0("../Data/Cluster/shapespace_passeriformes/param_chains/param_chain_passeriformes_50levels_chain", 2, ".rda"))
    param_chains[[2]] <- param_chain_passeriformes_50levels_chain1[[1]]
    load(paste0("../Data/Cluster/shapespace_passeriformes/param_chains/param_chain_passeriformes_50levels_chain", 3, ".rda"))
    param_chains[[3]] <- param_chain_passeriformes_50levels_chain1[[1]]
# }
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

>>>>

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
# for(i in 1:3) {
    load(paste0("../Data/Cluster/shapespace_passeriformes/param_chains/params_passerines_shapespace_8D_28levels_50k_chain", 1, ".rda"))
    param_chains[[1]] <- param_chain_passeriformes_50levels_chain1[[1]]
    load(paste0("../Data/Cluster/shapespace_passeriformes/param_chains/params_passerines_shapespace_8D_28levels_50k_chain", 2, ".rda"))
    param_chains[[2]] <- param_chain_passeriformes_50levels_chain1[[1]]
    load(paste0("../Data/Cluster/shapespace_passeriformes/param_chains/params_passerines_shapespace_8D_28levels_50k_chain", 3, ".rda"))
    param_chains[[3]] <- param_chain_passeriformes_50levels_chain1[[1]]
# }
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```
